|

### 2020-02-23 _other/tikz/tree/fs_tikz_gametree.tex
more tree changes

>>>>

\subsubsection{State Node and Choice Nodes}

States Nodes, Realizations, and then Continuous and Discrete Choice Nodes
\def\famm{5mm}
\def\fammlong{20mm}
\begin{center}
\begin{tikzpicture}[scale=1.5,font=\footnotesize]
\tikzstyle{level 1}=[level distance=\fammlong,sibling distance=\famm]
\tikzstyle{level 2}=[level distance=\fammlong,sibling distance=\famm]
\tikzstyle{level 3}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 4}=[level distance=\famm,sibling distance=\famm]
\tikzstyle{level 5}=[level distance=\famm,sibling distance=\famm]

% B Level 1 point
\node(0)[solid node, red, label=left:{
    $k,b$ chosen
    }]{}
[grow=right]
child{
    [grow=right]
    node(1)[solid node, blue, label=left:{
        $\Gamma$ realized 
        }]{}
    edge from parent
        [draw=none]
    child{
        [grow=right]
        node(2)[solid node, black, label=left:{$P1$}]{}
        edge from parent
            [draw=none]
        child{
            [black] node(11)[]{}
        }
        child{
            [grow=right]
            [white] node(12)[solid node, xshift=7.5, yshift=0]{}
            child{
                [black] node(21)[]{}
            }
            child{
                [grow=right]
                [white] node(22)[solid node, xshift=7.5, yshift=0]{}
                child {
                    [black] node(31)[]{}
                }
                child{
                    [black] node(32)[]{}
                }
                child{
                    [black] node(33)[]{}
                }
                child{
                    [black] node(34)[]{}
                }
            }
            child{
                [black] node(23)[]{}
            }
        }
        child{
            [black] node(13)[]{}
        }
    }
};
% information set
\draw[dashed, bend right]
    (11) to (13);
\draw[dashed, bend right]
    (21) to (23);
\draw[dotted, line width=0.35mm]
    (2) to (12);
\draw[dotted, line width=0.35mm]
    (12) to (22);
\end{tikzpicture}
\end{center}

### 2020-02-23 nontex/install/windows/fn_installations.Rmd
dcase larger fraction in case mode mathtools
more tree changes

- compile: *ctrl + alt + b*
- sync: *ctrl + alt + j*
- live save

@@

>>>>

- compile: *ctrl + alt + b*
- sync: *ctrl + alt + j*
- terminate pdflatex compile hang: *ctrl + shift + p; kill latex compiler process*
- live save

@@

- [sublime markdown Monokai Extended](https://github.com/jonschlinkert/sublime-monokai-extended), [sublime markdown extended](https://github.com/jonschlinkert/sublime-markdown-extended)
